---
title: "Generate Protein and RNA outputs for pathway analysis"
author: Alec Trub
output: html_notebook
---

#This is the initial code to run. It takes each list from omics and sorts them into seperate objects based on their treatment and directional change. Output limited by p value.

##Includes code to be used with other omics experiments that are unpublished
```{r}
library(tidyverse)
library(here)
library(readxl)
library(janitor)
library(cowplot)
library(viridis)
library(ggrepel)
library(enrichR)
library(rmarkdown)
library(knitr)
library(pander)
## install BiocManager if not installed
# if (!requireNamespace("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# ## install mixOmics
# BiocManager::install('mixOmics')
#devtools::install_github("hirscheylab/proteins")
library(plotly)
library(UpSetR)


```

#Protein

#import and add gene names
```{r}
proteins_statin <- read_xlsx(here::here( "data", "LFQProt.xlsx")) %>% 
  clean_names() %>% 
  mutate(description = str_pad(description, width = 200, side = "right", pad = " "), #pad to make str_extract work
         gn = str_extract(description,  "GN\\=[:graph:]+[:space:]")) %>% 
  select(gn, everything())

proteins_statin <- proteins_statin %>% 
  separate(gn, into = c("gn", "gene_name"), sep = "=", ) %>% 
  select(-gn)

proteins_statin <- proteins_statin %>% 
  mutate(diff = abundance_ratio_statin_control - abundance_ratio_hymeglusin_control) %>% 
  select(gene_name, diff, everything()) %>% 
  arrange(desc(diff))

labels <- proteins_statin %>% 
  filter(-log10(abundance_ratio_adj_p_value_statin_control) > 5, 
         abundance_ratio_statin_control < 20) %>% 
  subset() 

str_count(proteins_statin$description) %>% 
  hist()

sum(is.na(proteins_statin$gene_name))
```

#Seperate into data frames
```{r}
#set pval
pv = 0.05

#sort
statin_up <- proteins_statin %>% 
  filter(abundance_ratio_adj_p_value_statin_control <pv & abundance_ratio_statin_control < 100 & abundance_ratio_statin_control >1) %>% 
  pull(gene_name)

statin_down <- proteins_statin %>% 
  filter(abundance_ratio_adj_p_value_statin_control <pv & abundance_ratio_statin_control < 1) %>% 
  pull(gene_name)


hymeglusin_up <- proteins_statin %>% 
  filter(abundance_ratio_adj_p_value_hymeglusin_control <pv & abundance_ratio_hymeglusin_control < 100 & abundance_ratio_hymeglusin_control >1) %>% 
  pull(gene_name)

hymeglusin_down <- proteins_statin %>% 
  filter(abundance_ratio_adj_p_value_hymeglusin_control <pv & abundance_ratio_hymeglusin_control < 1) %>% 
  pull(gene_name)


metformin_up <- proteins_statin %>% 
  filter(abundance_ratio_adj_p_value_metformin_control <pv & abundance_ratio_metformin_control < 100 & abundance_ratio_metformin_control >1) %>% 
  pull(gene_name)

metformin_down <- proteins_statin %>% 
  filter(abundance_ratio_adj_p_value_metformin_control <pv & abundance_ratio_metformin_control < 1) %>% 
  pull(gene_name)


FASi_up <- proteins_statin %>% 
  filter(abundance_ratio_adj_p_value_fa_si_control <pv & abundance_ratio_fa_si_control < 100 & abundance_ratio_fa_si_control >1) %>% 
  pull(gene_name)

FASi_down <- proteins_statin %>% 
  filter(abundance_ratio_adj_p_value_fa_si_control <pv & abundance_ratio_fa_si_control < 1) %>% 
  pull(gene_name)

#Alternate sorting (based on prior sorting)
statin_lfq = proteins_statin %>%
  filter(abundance_ratio_hymeglusin_control < 100) %>%
  filter(abundance_ratio_adj_p_value_hymeglusin_control > 0.3 | log(abundance_ratio_hymeglusin_control) / log(abundance_ratio_statin_control < 0 )) %>%
  filter(abundance_ratio_adj_p_value_statin_control < 0.05)

```


#RNAseq compile

#import
```{r}
c = c(2,4,7,8)

df_statin <- read_excel("data/DifferentialExpression.xlsx", 
    sheet = "Statin_vs_Control")
df_statin = df_statin[c]
colnames(df_statin) = c("GeneName","StatinFC","Statin_pval","Statin_adjp")

df_hymeglusin <- read_excel("data/DifferentialExpression.xlsx", 
    sheet = "Hymeglusin_vs_Control")
df_hymeglusin = df_hymeglusin[c]
colnames(df_hymeglusin) = c("GeneName","hymeglusinFC","hymeglusin_pval","hymeglusin_adjp")

df_AICAR <- read_excel("data/DifferentialExpression.xlsx", 
    sheet = "AICAR_vs_Control")
df_AICAR = df_AICAR[c]
colnames(df_AICAR) = c("GeneName","AICARFC","AICAR_pval","AICAR_adjp")

df_C75 <- read_excel("data/DifferentialExpression.xlsx", 
    sheet = "C75_vs_Control")
df_C75 = df_C75[c]
colnames(df_C75) = c("GeneName","C75FC","C75_pval","C75_adjp")

```

#create dfs
```{r}

statin_up_rna <-df_statin %>% 
  filter(Statin_adjp <pv & StatinFC > 0) %>% 
  pull(GeneName)

statin_down_rna <-df_statin %>% 
  filter(Statin_adjp <pv & StatinFC < 0) %>% 
  pull(GeneName)


hymeglusin_up_rna <-df_hymeglusin %>% 
  filter(hymeglusin_adjp <pv & hymeglusinFC > 0) %>% 
  pull(GeneName)

hymeglusin_down_rna <-df_hymeglusin %>% 
  filter(hymeglusin_adjp <pv & hymeglusinFC < 0) %>% 
  pull(GeneName)


AICAR_up_rna <-df_AICAR %>% 
  filter(AICAR_adjp <pv & AICARFC > 0) %>% 
  pull(GeneName)

AICAR_down_rna <-df_AICAR %>% 
  filter(AICAR_adjp <pv & AICARFC < 0) %>% 
  pull(GeneName)


C75_up_rna <-df_C75 %>% 
  filter(C75_adjp <pv & C75FC > 0) %>% 
  pull(GeneName)

C75_down_rna <-df_C75 %>% 
  filter(C75_adjp <pv & C75FC < 0) %>% 
  pull(GeneName)

```



#PhosphoTMTProtein

#import
```{r}
#import 24 hour protein changes from TMT experiment
df_statin <- read_xlsx(here::here( "data", "tmtproteins.xlsx"), skip = 2, col_names = F) %>% 
  clean_names()%>% 
  select(2,21:26)


colnames(df_statin) = c("gene_name","StatinFC","Statinpv","Statinapv","HymeFC","Hymepv","Hymeapv")


```








#get genes
```{r}

statin_up_tmt <- df_statin %>% 
  filter(Statinpv <pv & StatinFC>0) %>% 
  pull(gene_name)

statin_down_tmt <- df_statin %>% 
  filter(Statinpv <pv & StatinFC<0) %>% 
  pull(gene_name)

hymeglusin_up_tmt <- df_statin %>% 
  filter(Hymepv <pv & HymeFC>0) %>% 
  pull(gene_name)

hymeglusin_down_tmt <- df_statin %>% 
  filter(Hymepv <pv & HymeFC<0) %>% 
  pull(gene_name)


```




#Export

```{r}
write.table(statin_up, "export/prot_statin_up.csv", row.names = F, col.names = F)
write.table(statin_down, "export/prot_statin_down.csv", row.names = F, col.names = F)
write.table(hymeglusin_up, "export/prot_hymeglusin_up.csv", row.names = F, col.names = F)
write.table(hymeglusin_down, "export/prot_hymeglusin_down.csv", row.names = F, col.names = F)
write.table(metformin_up, "export/prot_metformin_up.csv", row.names = F, col.names = F)
write.table(metformin_down, "export/prot_metformin_down.csv", row.names = F, col.names = F)
write.table(FASi_up, "export/prot_FASi_up.csv", row.names = F, col.names = F)
write.table(FASi_down, "export/prot_FASi_down.csv", row.names = F, col.names = F)


write.table(statin_up_rna, "export/RNA_statin_up.csv", row.names = F, col.names = F)
write.table(statin_down_rna, "export/RNA_statin_down.csv", row.names = F, col.names = F)
write.table(hymeglusin_up_rna, "export/RNA_hymeglusin_up.csv", row.names = F, col.names = F)
write.table(hymeglusin_down_rna, "export/RNA_hymeglusin_down.csv", row.names = F, col.names = F)
write.table(AICAR_up_rna, "export/RNA_AICAR_up.csv", row.names = F, col.names = F)
write.table(AICAR_down_rna, "export/RNA_AICAR_down.csv", row.names = F, col.names = F)
write.table(C75_up_rna, "export/RNA_FASi_up.csv", row.names = F, col.names = F)
write.table(C75_down_rna, "export/RNA_FASi_down.csv", row.names = F, col.names = F)


write.table(statin_up_tmt, "export/tmt_statin_up.csv", row.names = F, col.names = F)
write.table(statin_down_tmt, "export/tmt_statin_down.csv", row.names = F, col.names = F)
write.table(hymeglusin_up_tmt, "export/tmt_hymeglusin_up.csv", row.names = F, col.names = F)
write.table(hymeglusin_down_tmt, "export/tmt_hymeglusin_down.csv", row.names = F, col.names = F)
```

