---
title: "Generate Upsetter Plot Using Enrichr dataframes"
author: Alec Trub
output: html_notebook
---
# Run "Lists", then "Enricher" first. This takes the master list from Enricher and creats an upsetter plot to compare overlapping and distinct pathways changes
```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(cowplot)
library(viridis)
library(ggrepel)
library(enrichR)
library(rmarkdown)
library(knitr)
library(pander)
## install BiocManager if not installed
# if (!requireNamespace("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# ## install mixOmics
# BiocManager::install('mixOmics')
#devtools::install_github("hirscheylab/proteins")
library(plotly)
library(UpSetR)


```

#Create Master list/data frame
```{r}
df_upsetter = master_list %>% 
  separate(col = 1, into = c("treatment","direction","omic"), sep = "_" ) %>% 
  filter(Adjusted.P.value < 0.05)
colnames(df_upsetter)[5] = "term"
df_upsetter = df_upsetter %>%
  separate(col = term, into = c("term", "GO"), sep = "\\(")

```


#Create Lists of pathways for each omic
```{r}

#LFQ-Only statin and hymeglusin conditions
list_upsetter_LFQ = list(
statin_up = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "up" & omic == "protein"),term)),
statin_down = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "down" & omic == "protein"),term)),
hymeglusin_up = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "up" & omic == "protein"),term)),
hymeglusin_down = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "down" & omic == "protein"),term))
)
  
#LFQ
list_upsetter_LFQ_all = list(
statin_up = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "up" & omic == "protein"),term)),
statin_down = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "down" & omic == "protein"),term)),
hymeglusin_up = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "up" & omic == "protein"),term)),
hymeglusin_down = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "down" & omic == "protein"),term)),
ampk_up = as.list(pull(filter(df_upsetter, treatment == "ampk" & direction == "up" & omic == "protein"),term)),
ampk_down = as.list(pull(filter(df_upsetter, treatment == "ampk" & direction == "down" & omic == "protein"),term))#,
#fasi_up = as.list(pull(filter(df_upsetter, treatment == "fasi" & direction == "up" & omic == "protein"),term)),
#fasi_down = as.list(pull(filter(df_upsetter, treatment == "fasi" & direction == "down" & omic == "protein"),term))
  )


#RNA-statin and hyme only
list_upsetter_rna = list(
statin_up = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "up" & omic == "rna"),term)),
statin_down = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "down" & omic == "rna"),term)),
hymeglusin_up = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "up" & omic == "rna"),term)),
hymeglusin_down = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "down" & omic == "rna"),term))
)
  
#RNA
list_upsetter_rna_all = list(
statin_up = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "up" & omic == "rna"),term)),
statin_down = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "down" & omic == "rna"),term)),
hymeglusin_up = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "up" & omic == "rna"),term)),
hymeglusin_down = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "down" & omic == "rna"),term)),
ampk_up = as.list(pull(filter(df_upsetter, treatment == "ampk" & direction == "up" & omic == "rna"),term)),
ampk_down = as.list(pull(filter(df_upsetter, treatment == "ampk" & direction == "down" & omic == "rna"),term))#,
#fasi_up = as.list(pull(filter(df_upsetter, treatment == "fasi" & direction == "up" & omic == "rna"),term)),
#fasi_down = as.list(pull(filter(df_upsetter, treatment == "fasi" & direction == "down" & omic == "rna"),term))
)

#TMTProt - no other conditions tested
list_upsetter_tmt = list(
statin_up = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "up" & omic == "tmt"),term)),
statin_down = as.list(pull(filter(df_upsetter, treatment == "statin" & direction == "down" & omic == "tmt"),term)),
hymeglusin_up = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "up" & omic == "tmt"),term)),
hymeglusin_down = as.list(pull(filter(df_upsetter, treatment == "hymeglusin" & direction == "down" & omic == "tmt"),term))
)
```



#UpSetR
From: https://cran.r-project.org/web/packages/UpSetR/vignettes/basic.usage.html   
```{r}
##LFQ
#Statin v Hyme
#Rename sets for graphing
names(list_upsetter_LFQ) = c("Statin Increase", "Statin Decrease", "Hymeglusin Increase", "Hymeglusin Decrease")
names(list_upsetter_LFQ_all) = c("Statin Increase", "Statin Decrease", "Hymeglusin Increase", "Hymeglusin Decrease", "Metformin Increase", "Metformin Decrease")

UpLFQ = upset(fromList(list_upsetter_LFQ),
      order.by = "freq", 
      nsets = 8, 
      number.angles = 30, 
      point.size = 3, 
      line.size = 1, 
      mainbar.y.label = "Pathways Intersections", 
      sets.x.label = "Pathways Per Condition",
      text.scale = c(1.5, 1.3, 1, 1, 1.5, 1.3)
      
)



UpLFQall = upset(fromList(list_upsetter_LFQ_all),
      order.by = "freq", 
      nsets = 8, 
      number.angles = 30, 
      point.size = 3, 
      line.size = 1, 
      mainbar.y.label = "Pathway Intersections", 
      sets.x.label = "Pathway Per Condition",
      text.scale = c(1.5, 1.3, 1, 1, 1.5, 1.3)
)


##rna
#Statin v Hyme
upset(fromList(list_upsetter_rna),
      order.by = "freq", 
      nsets = 8, 
      number.angles = 30, 
      point.size = 3, 
      line.size = 1, 
      mainbar.y.label = "Pathways Intersections", 
      sets.x.label = "Pathways Per Condition",
      #text.scale = c(1.3, 1.3, 1, 1, 1, 0.75)
)

upset(fromList(list_upsetter_rna_all),
      order.by = "freq", 
      nsets = 8, 
      number.angles = 30, 
      point.size = 3, 
      line.size = 1, 
      mainbar.y.label = "Pathway Intersections", 
      sets.x.label = "Pathway Per Condition",
      #text.scale = c(1.3, 1.3, 1, 1, 1, 0.75)
)

##TMTProt
#Statin v Hyme
upset(fromList(list_upsetter_tmt),
      order.by = "freq", 
      nsets = 8, 
      number.angles = 30, 
      point.size = 3, 
      line.size = 1, 
      mainbar.y.label = "Pathways Intersections", 
      sets.x.label = "Pathways Per Condition",
      #text.scale = c(1.3, 1.3, 1, 1, 1, 0.75)
)

#reset names to prevent breaking code below
names(list_upsetter_LFQ) =c("statin_up", "statin_down", "hymeglusin_up", "hymeglusin_down")
names(list_upsetter_LFQ_all) = c("statin_up", "statin_down", "hymeglusin_up", "hymeglusin_down", "ampk_up", "ampk_down")


#Export Code
# svg("export/UpSetter LFQ AMPK.svg")
# UpLFQall
# dev.off()

```

#statin v hyme only breakout lists
```{r}

##Statin v Hyme only
#breakout statin up hyme down
suhd_LFQ_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_LFQ[["statin_up"]], 
         term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ[["statin_down"]],
         !term %in% list_upsetter_LFQ[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

su_LFQ_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_LFQ[["statin_up"]], 
         !term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ[["statin_down"]],
         !term %in% list_upsetter_LFQ[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()
hd_LFQ_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ[["statin_up"]], 
         term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ[["statin_down"]],
         !term %in% list_upsetter_LFQ[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

#breakout statin down hyme up
sdhu_LFQ_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ[["statin_up"]], 
         !term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         term %in% list_upsetter_LFQ[["statin_down"]],
         term %in% list_upsetter_LFQ[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sd_LFQ_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ[["statin_up"]], 
         !term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         term %in% list_upsetter_LFQ[["statin_down"]],
         !term %in% list_upsetter_LFQ[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

hu_LFQ_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ[["statin_up"]], 
         !term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ[["statin_down"]],
         term %in% list_upsetter_LFQ[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sdhd_LFQ_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ[["statin_up"]], 
         term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         term %in% list_upsetter_LFQ[["statin_down"]],
         !term %in% list_upsetter_LFQ[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

suhu_LFQ_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_LFQ[["statin_up"]], 
         !term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ[["statin_down"]],
         term %in% list_upsetter_LFQ[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

LFQ_list = list(suhd_LFQ_E = suhd_LFQ_E, su_LFQ_E = su_LFQ_E, hd_LFQ_E = hd_LFQ_E, sdhu_LFQ_E = sdhu_LFQ_E, sd_LFQ_E = sd_LFQ_E, sdhd_LFQ_E = sdhd_LFQ_E, suhu_LFQ_E = suhu_LFQ_E, hu_LFQ_E = hu_LFQ_E)
```

#statin v hyme with AMPK breakout lists
```{r}

##Statin v Hyme only
#breakout statin up hyme down
suhd_LFQ_AMPK <- df_upsetter %>% 
  filter(term %in% list_upsetter_LFQ_all[["statin_up"]], 
         term %in% list_upsetter_LFQ_all[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ_all[["statin_down"]],
         !term %in% list_upsetter_LFQ_all[["hymeglusin_up"]],
         term %in% list_upsetter_LFQ_all[["ampk_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

su_LFQ_AMPK <- df_upsetter %>% 
  filter(term %in% list_upsetter_LFQ_all[["statin_up"]], 
         !term %in% list_upsetter_LFQ_all[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ_all[["statin_down"]],
         !term %in% list_upsetter_LFQ_all[["hymeglusin_up"]],
         term %in% list_upsetter_LFQ_all[["ampk_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()
hd_LFQ_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ[["statin_up"]], 
         term %in% list_upsetter_LFQ[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ[["statin_down"]],
         !term %in% list_upsetter_LFQ[["hymeglusin_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

#breakout statin down hyme up
sdhu_LFQ_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ_all[["statin_up"]], 
         !term %in% list_upsetter_LFQ_all[["hymeglusin_down"]],
         term %in% list_upsetter_LFQ_all[["statin_down"]],
         term %in% list_upsetter_LFQ_all[["hymeglusin_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_up"]],
         term %in% list_upsetter_LFQ_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sd_LFQ_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ_all[["statin_up"]], 
         !term %in% list_upsetter_LFQ_all[["hymeglusin_down"]],
         term %in% list_upsetter_LFQ_all[["statin_down"]],
         !term %in% list_upsetter_LFQ_all[["hymeglusin_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_up"]],
         term %in% list_upsetter_LFQ_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

hu_LFQ_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ_all[["statin_up"]], 
         !term %in% list_upsetter_LFQ_all[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ_all[["statin_down"]],
         term %in% list_upsetter_LFQ_all[["hymeglusin_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sdhd_LFQ_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_LFQ_all[["statin_up"]], 
         term %in% list_upsetter_LFQ_all[["hymeglusin_down"]],
         term %in% list_upsetter_LFQ_all[["statin_down"]],
         !term %in% list_upsetter_LFQ_all[["hymeglusin_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_up"]],
         term %in% list_upsetter_LFQ_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

suhu_LFQ_AMPK <- df_upsetter %>% 
  filter(term %in% list_upsetter_LFQ_all[["statin_up"]], 
         !term %in% list_upsetter_LFQ_all[["hymeglusin_down"]],
         !term %in% list_upsetter_LFQ_all[["statin_down"]],
         term %in% list_upsetter_LFQ_all[["hymeglusin_up"]],
         term %in% list_upsetter_LFQ_all[["ampk_up"]],
         !term %in% list_upsetter_LFQ_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

LFQ_AMPK_list = list(suhd_LFQ_AMPK = suhd_LFQ_AMPK, su_LFQ_AMPK = su_LFQ_AMPK, hd_LFQ_AMPK = hd_LFQ_AMPK, sdhu_LFQ_AMPK = sdhu_LFQ_AMPK, sd_LFQ_AMPK = sd_LFQ_AMPK, sdhd_LFQ_AMPK = sdhd_LFQ_AMPK, suhu_LFQ_AMPK = suhu_LFQ_AMPK, hu_LFQ_AMPK = hu_LFQ_AMPK)
```

#RNA
```{r}

##Statin v Hyme only
#breakout statin up hyme down
suhd_rna_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_rna[["statin_up"]], 
         term %in% list_upsetter_rna[["hymeglusin_down"]],
         !term %in% list_upsetter_rna[["statin_down"]],
         !term %in% list_upsetter_rna[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

su_rna_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_rna[["statin_up"]], 
         !term %in% list_upsetter_rna[["hymeglusin_down"]],
         !term %in% list_upsetter_rna[["statin_down"]],
         !term %in% list_upsetter_rna[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()
hd_rna_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna[["statin_up"]], 
         term %in% list_upsetter_rna[["hymeglusin_down"]],
         !term %in% list_upsetter_rna[["statin_down"]],
         !term %in% list_upsetter_rna[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

#breakout statin down hyme up
sdhu_rna_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna[["statin_up"]], 
         !term %in% list_upsetter_rna[["hymeglusin_down"]],
         term %in% list_upsetter_rna[["statin_down"]],
         term %in% list_upsetter_rna[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sd_rna_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna[["statin_up"]], 
         !term %in% list_upsetter_rna[["hymeglusin_down"]],
         term %in% list_upsetter_rna[["statin_down"]],
         !term %in% list_upsetter_rna[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

hu_rna_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna[["statin_up"]], 
         !term %in% list_upsetter_rna[["hymeglusin_down"]],
         !term %in% list_upsetter_rna[["statin_down"]],
         term %in% list_upsetter_rna[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sdhd_rna_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna[["statin_up"]], 
         term %in% list_upsetter_rna[["hymeglusin_down"]],
         term %in% list_upsetter_rna[["statin_down"]],
         !term %in% list_upsetter_rna[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

suhu_rna_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_rna[["statin_up"]], 
         !term %in% list_upsetter_rna[["hymeglusin_down"]],
         !term %in% list_upsetter_rna[["statin_down"]],
         term %in% list_upsetter_rna[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

rna_list = list(suhd_rna_E = suhd_rna_E, su_rna_E = su_rna_E, hd_rna_E = hd_rna_E, sdhu_rna_E = sdhu_rna_E, sd_rna_E = sd_rna_E, sdhd_rna_E = sdhd_rna_E, suhu_rna_E = suhu_rna_E, hu_rna_E = hu_rna_E)
```

#statin v hyme with AMPK breakout lists
```{r}

##Statin v Hyme only
#breakout statin up hyme down
suhd_rna_AMPK <- df_upsetter %>% 
  filter(term %in% list_upsetter_rna_all[["statin_up"]], 
         term %in% list_upsetter_rna_all[["hymeglusin_down"]],
         !term %in% list_upsetter_rna_all[["statin_down"]],
         !term %in% list_upsetter_rna_all[["hymeglusin_up"]],
         term %in% list_upsetter_rna_all[["ampk_up"]],
         !term %in% list_upsetter_rna_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

su_rna_AMPK <- df_upsetter %>% 
  filter(term %in% list_upsetter_rna_all[["statin_up"]], 
         !term %in% list_upsetter_rna_all[["hymeglusin_down"]],
         !term %in% list_upsetter_rna_all[["statin_down"]],
         !term %in% list_upsetter_rna_all[["hymeglusin_up"]],
         term %in% list_upsetter_rna_all[["ampk_up"]],
         !term %in% list_upsetter_rna_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()
hd_rna_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna[["statin_up"]], 
         term %in% list_upsetter_rna[["hymeglusin_down"]],
         !term %in% list_upsetter_rna[["statin_down"]],
         !term %in% list_upsetter_rna[["hymeglusin_up"]],
         !term %in% list_upsetter_rna_all[["ampk_up"]],
         !term %in% list_upsetter_rna_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

#breakout statin down hyme up
sdhu_rna_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna_all[["statin_up"]], 
         !term %in% list_upsetter_rna_all[["hymeglusin_down"]],
         term %in% list_upsetter_rna_all[["statin_down"]],
         term %in% list_upsetter_rna_all[["hymeglusin_up"]],
         !term %in% list_upsetter_rna_all[["ampk_up"]],
         term %in% list_upsetter_rna_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sd_rna_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna_all[["statin_up"]], 
         !term %in% list_upsetter_rna_all[["hymeglusin_down"]],
         term %in% list_upsetter_rna_all[["statin_down"]],
         !term %in% list_upsetter_rna_all[["hymeglusin_up"]],
         !term %in% list_upsetter_rna_all[["ampk_up"]],
         term %in% list_upsetter_rna_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

hu_rna_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna_all[["statin_up"]], 
         !term %in% list_upsetter_rna_all[["hymeglusin_down"]],
         !term %in% list_upsetter_rna_all[["statin_down"]],
         term %in% list_upsetter_rna_all[["hymeglusin_up"]],
         !term %in% list_upsetter_rna_all[["ampk_up"]],
         !term %in% list_upsetter_rna_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sdhd_rna_AMPK <- df_upsetter %>% 
  filter(!term %in% list_upsetter_rna_all[["statin_up"]], 
         term %in% list_upsetter_rna_all[["hymeglusin_down"]],
         term %in% list_upsetter_rna_all[["statin_down"]],
         !term %in% list_upsetter_rna_all[["hymeglusin_up"]],
         !term %in% list_upsetter_rna_all[["ampk_up"]],
         term %in% list_upsetter_rna_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

suhu_rna_AMPK <- df_upsetter %>% 
  filter(term %in% list_upsetter_rna_all[["statin_up"]], 
         !term %in% list_upsetter_rna_all[["hymeglusin_down"]],
         !term %in% list_upsetter_rna_all[["statin_down"]],
         term %in% list_upsetter_rna_all[["hymeglusin_up"]],
         term %in% list_upsetter_rna_all[["ampk_up"]],
         !term %in% list_upsetter_rna_all[["ampk_down"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

rna_AMPK_list = list(suhd_rna_AMPK = suhd_rna_AMPK, su_rna_AMPK = su_rna_AMPK, hd_rna_AMPK = hd_rna_AMPK, sdhu_rna_AMPK = sdhu_rna_AMPK, sd_rna_AMPK = sd_rna_AMPK, sdhd_rna_AMPK = sdhd_rna_AMPK, suhu_rna_AMPK = suhu_rna_AMPK, hu_rna_AMPK = hu_rna_AMPK)
```

#TMT breakdown lists
```{r}

##Statin v Hyme only
#breakout statin up hyme down
suhd_tmt_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_tmt[["statin_up"]], 
         term %in% list_upsetter_tmt[["hymeglusin_down"]],
         !term %in% list_upsetter_tmt[["statin_down"]],
         !term %in% list_upsetter_tmt[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

su_tmt_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_tmt[["statin_up"]], 
         !term %in% list_upsetter_tmt[["hymeglusin_down"]],
         !term %in% list_upsetter_tmt[["statin_down"]],
         !term %in% list_upsetter_tmt[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()
hd_tmt_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_tmt[["statin_up"]], 
         term %in% list_upsetter_tmt[["hymeglusin_down"]],
         !term %in% list_upsetter_tmt[["statin_down"]],
         !term %in% list_upsetter_tmt[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

#breakout statin down hyme up
sdhu_tmt_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_tmt[["statin_up"]], 
         !term %in% list_upsetter_tmt[["hymeglusin_down"]],
         term %in% list_upsetter_tmt[["statin_down"]],
         term %in% list_upsetter_tmt[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sd_tmt_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_tmt[["statin_up"]], 
         !term %in% list_upsetter_tmt[["hymeglusin_down"]],
         term %in% list_upsetter_tmt[["statin_down"]],
         !term %in% list_upsetter_tmt[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

hu_tmt_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_tmt[["statin_up"]], 
         !term %in% list_upsetter_tmt[["hymeglusin_down"]],
         !term %in% list_upsetter_tmt[["statin_down"]],
         term %in% list_upsetter_tmt[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

sdhd_tmt_E <- df_upsetter %>% 
  filter(!term %in% list_upsetter_tmt[["statin_up"]], 
         term %in% list_upsetter_tmt[["hymeglusin_down"]],
         term %in% list_upsetter_tmt[["statin_down"]],
         !term %in% list_upsetter_tmt[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

suhu_tmt_E <- df_upsetter %>% 
  filter(term %in% list_upsetter_tmt[["statin_up"]], 
         !term %in% list_upsetter_tmt[["hymeglusin_down"]],
         !term %in% list_upsetter_tmt[["statin_down"]],
         term %in% list_upsetter_tmt[["hymeglusin_up"]]) %>% 
  drop_na(term) %>% 
  pull(term) %>% 
  unique()

tmt_list = list(suhd_tmt_E = suhd_tmt_E, su_tmt_E = su_tmt_E, hd_tmt_E = hd_tmt_E, sdhu_tmt_E = sdhu_tmt_E, sd_tmt_E = sd_tmt_E, sdhd_tmt_E = sdhd_tmt_E, suhu_tmt_E = suhu_tmt_E, hu_tmt_E = hu_tmt_E)
```




